Methods for Polyphonic Music Transcription

### 2013-12-11 paper/paper.tex
Made nmf more testable, some paper edits

We implemented a NMF transcription system. We used constructed our $W$ matrix by concatenating spectra from training recording. We tried both a standard STFT spectrogram and constant Q transform spectrogram. We use the normalizations proposed by \citet{niedermayer2008non}. After creating the $W$ matrix, we calculate the $H$ matrix using the previously-defined multiplicative update rule. The $H$ matrix is smoothed using a median filter and thresholded.

@@

\section{Individual Effort}
\begin{description}
\item[$\bullet$ Jeremy] wrote and evaluted the SVM method in \citet{poliner2006discriminative}, the non-negative matrix factorization method in \citet{abdallah2004polyphonic}, the AdaBoost method in \citet{boogaart2009note}, and wrote the paper.
\item[$\bullet$ Mark] implemented the hidden Markov model and error measures in \citet{poliner2006discriminative}, evaluated the methods, and wrote the paper.
\item[$\bullet$ Paul] implemented the non-negative matrix factorization method in \citet{abdallah2004polyphonic} and wrote the paper.
\end{description}

>>>>

We implemented a NMF transcription system. We used constructed our $W$ matrix by concatenating spectra from training recording. We tried both a standard STFT spectrogram and constant Q transform spectrogram. We use the normalizations proposed by \citet{niedermayer2008non}. After creating the $W$ matrix, we calculate the $H$ matrix using the previously-defined multiplicative update rule. The $H$ matrix is smoothed using a median filter and thresholded. The STFT $W$ matrix and a sample of the smoothed $H$ are shown in figure 2.

@@

\section{Individual Effort}
\begin{description}
\item[$\bullet$ Jeremy] wrote and evaluted the SVM method in \citet{poliner2006discriminative}, the non-negative matrix factorization method in \citet{abdallah2004polyphonic}, the AdaBoost method in \citet{boogaart2009note}, and wrote the paper.
\item[$\bullet$ Mark] implemented the hidden Markov model and error measures in \citet{poliner2006discriminative}, evaluated the methods, and wrote the paper.
\item[$\bullet$ Paul] implemented the non-negative matrix factorization methods in \citet{abdallah2004polyphonic} and \citet{niedermayer2008non} and wrote the paper.
\end{description}
